(Working Title) Stellar and Planetary Properties of \KT\ \Ci\ Candidates and Validation of \Nvalidated\ Systems, (Including a Planet Receiving Earth-like Insolation?)

### 2015-03-10 ms.tex
added reference; more tdm edits

\section{False Positive Analysis}
As has been well known from the early days of transit searches, it is
possible for an eclipsing binary star to masquerade as a transiting
planet if (a) it is a highly grazing eclipse, or (b) the binary system
comprises only a small fraction of the total light in the photometric
aperture, resulting in a diluted eclipse depth.
When possible, such astrophsycial false positive scenarios are traditionally
ruled out by detailed follow-up observations, such as high-resolution
imaging or radial-velocity measurements.
However, the \kep\ mission, with its thousands of planet candidates
around mostly faint stars, necessitated a paradigm shift---a move
toward probabilistic interpretation of transit signals, rather than
comprehensive follow-up of each individual candidate.

\citet{Morton12} presented an automated method to calculate the
probability that a planet candidate might be caused by an
astrophysical false positive.
This method uses population simulations of the light curves of
of false positive scenarios and true transiting planets to quantify
the typical shape of each, comparing to the observed transit shape.
It then combines this information with observationally motivated prior
assumptions about the populations of field stars, the properties of
multiple star systems, and the occurrence rate of planets as determined
from \kep\ \citet{Fressin13}, in order to determine the probability that
the observed signal may be a false positive.
Similar in spirit to other published methods of
probabilistic validation, such as Blender \citep{} and PASTIS
\citep{}, it has the advantage of being computationally less demanding
and fully automated, and thus easily applied in batch to a large
number of candidates.

In this work, we use
\texttt{vespa}\footnote{\url{http://github.com/timothydmorton/vespa}},
a new general-purpose implementation of the \citet{Morton12} procedure, 
to calculate false positive probabilities (FPPs) for each of these 
K2 candidates.  We impose the following constraints on false positive
scenarios:
\begin{itemize}
\item A chance-aligned eclipsing binary system may reside within
a sky area equivalent to 8 arcsecond radius of the target star.
\item The maximum allowed depth of a potential secondary eclipse event,
determined as the most significantly detected signal at the same
period of the planet candidate, once the primary transit is masked out.
\item High-resolution imaging constraints, where available (see below)
\end{itemize}

@@

We emphasize that the majority of these planets were validated based 
solely on the transit signal, with no need for follow-up imaging.  This
demonstrates the utility of \texttt{vespa} analysis, which will be
crucial to interpreting future \kt\ detected candidates and prioritizing
follow-up observing efforts.

>>>>

\section{False Positive Analysis}
As has been well known from the early days of transit searches, it is
possible for an eclipsing binary star to masquerade as a transiting
planet if (a) it is a highly grazing eclipse, or (b) the binary system
comprises only a small fraction of the total light in the photometric
aperture, resulting in a diluted eclipse depth.
When possible, such astrophsycial false positive scenarios are traditionally
ruled out by detailed follow-up observations, often a combination of 
high-resolution imaging and radial-velocity measurements.
However, the \kep\ mission, with its thousands of planet candidates
around mostly faint stars, necessitated a paradigm shift---a move
toward probabilistic interpretation of transit signals, rather than
comprehensive follow-up of each individual candidate.

\citet{Morton12} presented an automated method to calculate the
probability that a planet candidate might be caused by an
astrophysical false positive.
This method uses population simulations of the light curves of
of false positive scenarios and true transiting planets to quantify
the typical shape of each, comparing to the observed transit shape.
It then combines this information with observationally motivated prior
assumptions about the populations of field stars, the properties of
multiple star systems, and the occurrence rate of planets as determined
from \kep\ \citep{Fressin13}, in order to determine the probability that
the observed signal may be a false positive.
Similar in spirit to other published methods of
probabilistic validation, such as Blender \citep{} and PASTIS
\citep{}, it has the advantage of being computationally less demanding
and fully automated, and thus easily applied in batch to a large
number of candidates.

In this work, we use
\texttt{vespa}\footnote{\url{http://github.com/timothydmorton/vespa}},
a new general-purpose implementation of the \citet{Morton12} procedure, 
to calculate false positive probabilities (FPPs) for each of these 
K2 candidates.  We impose the following constraints on false positive
scenarios:
\begin{itemize}
\item A chance-aligned eclipsing binary system may reside anywhere within
an 8 arcsecond radius from the target star.
\item The maximum allowed depth of a potential secondary eclipse event,
determined as the most significantly detected signal at the same
period of the planet candidate, once the primary transit is masked out.
\item High-resolution imaging constraints, where available (see below)
\end{itemize}

@@

We emphasize that the majority of these planets were validated based 
solely on the transit signal, with no need for follow-up imaging.  This
demonstrates the utility of \texttt{vespa} analysis, which will be
crucial to interpreting future \KT\ detected candidates and prioritizing
follow-up observing efforts.
